Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Paper
Work in progress.

            \begin{figure}
                \includegraphics[width=\linewidth, frame]{img/fig_fun_ackley.pdf}
                \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
                \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=\linewidth, frame]{img/fig_fun_griewank.pdf}
                \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=\linewidth, frame]{img/fig_fun_rastrigin.pdf}
                \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=\linewidth, frame]{img/fig_fun_sphere.pdf}
                \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 5 Dimensions.} \label{fig.fun_rosenbrock_5d}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 10 Dimensions.} \label{fig.fun_rosenbrock_10d}
                \end{figure}

>>>>

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_ackley.pdf}
                \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
                \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_griewank.pdf}
                \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rastrigin.pdf}
                \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_sphere.pdf}
                \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 5 Dimensions.} \label{fig.fun_rosenbrock_5d}
                \end{figure}

@@

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 10 Dimensions.} \label{fig.fun_rosenbrock_10d}
                \end{figure}
